\plaintitle

### 2016-05-27 cscw/papers/2017/labor/trackingWork.tex
cleanup

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the processes involved in making work into tasks, or \textbf{discretization},
in ``\nameref{sec:MakingGigsWork}'';
\item the outcomes of that discretization, both on the work itself as well as the workers,
in ``\nameref{sec:Fallout}'';
and finally
\item the results of these forces; namely the turning of work toward \textbf{factories},
which we will discuss in ``\nameref{sec:Factorization}''.
\end{enumerate}

@@

@@

\subsubsection{Decomposition}\label{sec:decomposition}
Scholarship describing and exploring
the decomposition of tasks is perhaps the most established of the above areas among HCI researchers;
\citeauthor{bernsteinSoylent} made early contributions to this area with \textit{Soylent}
(by coining and employing the ``find--fix--verify'' approach)
\cite{bernsteinSoylent}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work might be readily interrupted
\cite{cheng2015break}.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work
by exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While this work doesn't strictly fall under ``crowdsourcing'',
the major contributions here
seem uncontroversially to be inspired by the design of crowd work.

@@

Work decomposition is far from new;
``decomposition'' generally illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{silberman2010ethics} in particular foresaw this danger and warned of it in
\citeyear{silberman2010ethics}
\cite{crowdworkFuture,silberman2010ethics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in his documentary work
\citetitle{riisOtherSideLives}
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

@@

Here, \citeauthor{hu1961parallel}'s work,
saying of assembly line work that
``It is assumed that men are of equal ability and every man can do any of the $n$ jobs'',
parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,
and indeed the study of factory and mass manufacturing labor through the \nth{20} century,
substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,
and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

@@

@@

% \textit{There's a reference to something that's \textbf{not} 99designs,
% that describes a call for scientific solutions/designs to solve some problem
% that the requesters have.
% Honestly it's killing me that I can't remember the name,
% and I need to find this before I do anything productive ever again.}
% \msb{netflix prize?}
% that's an interesting example in the same vein as what i'm thinking about, but this is a whole business of it
% \textbf{INNOCENTIVE} oh my gosh it just clicked my life is complete right now at 9:54am.
% I don't even need to submit anymore.
% I'm satisfied having pulled this strand of a memory out of my brain.

The HCI community is perhaps most familiar with examples such as
Innocentive,
Uber, Lyft,
and Amazon Mechanical Turk (AMT),
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.

% The insight here seems to have been that
% a substantial amount of work does not necessarily need to be done in collocated space,
% but can be done from one's own home or other space arranged by the worker.
% Moreover, by shifting the workplace into the worker's domain,
% the cost of capital involved in that work can more easily be placed on workers' backs
% \msb{I don't think that was the original motivation for AMT or Uber --- it was about reaching people who could not otherwise join the labor force for Amazon's data cleaning or for taxi-ing.}.
% I didn't mean that this was some insight that Uber or Lyft had, but that this was some part of what makes Uber work;
% i would argue categorically that these companies wouldn't functionally work if they weren't able to obviate the 
% maintenance costs that a factory owner would associate with their capital (e.g. auto costs)
While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
(inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
these new systems go further
by framing ownership and responsibility for costs
(e.g. automotive maintenance)
on drivers.
In our fieldwork, we discovered many longtime ``on--demand'' drivers
(affiliated with platforms such as Uber and Lyft)
who readily voiced frustration with the costs of
frequent oil changes and the unexpected replacement of expensive parts.
Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
textile workers were given the source material with which to work,
but were generally expected to use their own sewing materials and work in their own homes
\cite{hapke2004sweatshop}.

% \subsection{Discretization and Routinization}
% \subsubsection{Decomposition}\label{sec:decomposition}
Distributing work in method described above may be thought of as vertically slicing work such that 
each person is responsible for the whole task
--- making a whole garment or being responsible for driving in a single neighborhood.
Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable.
Textile work being a salient example,
some seamstresses might be better than others at the same task,
making this framing of the work initially problematic.

@@

Opening the door to more discrete modules of work known as tasks 
% Work has become discretized in the last 10 years, particularly in the information work sector.
Contributions such as
``find--fix--verify'' % (described in \citetitle{bernsteinSoylent})
and
``Cascade'' % (described in \citetitle{chilton2013cascade})
make it easier to assign smaller components of work to myriad workers and
recompose the constituent parts into something more complex
\cite{bernsteinSoylent,chilton2013cascade}.
Some work has taken special interest in the process of breaking tasks down into more manageable parts
% Some work has even turned to break it down'',
inasmuch as decomposing what we might call ``macro'' tasks into microtasks,
both for the purposes of crowd--sourcing in the sense of out--sourcing work
as well as ``selfsourcing''
\cite{cheng2015break,selfsourcingTeevan2014}.

The parallels between this kind of work and
historical piecework of the turn of the \nth{20} century
is by no means new.

The \textbf{discretization} and decomposition of work certainly facilitates
breaking tasks down,
parallelizing work,
and getting more done across a broader array of people;
but the key advantage in turning macro tasks 
into many micro tasks is that we can make that work \textit{routine}.

By making larger bodies of work less contextually situated,
we can define processes that make that work
and the instructions thereof
useful for virtually anyone with shared cultural or intellectual background.

routinization can be seen in the contemporary in work--flows
\cite{foundry,bernsteinSoylent}.
% [\textit{There are various papers that talk about creating a work--flow;
% maybe this is where FFV belongs? Foundry?}].

@@

Piecework emerged at the turn of the \nth{20} century,
right at the time that telecommunications began to boom in the United States. % too far a reach?
\textit{Did telecom enable remote management?}

>>>>

\section{Case Studies}
The existing body of research has shed light on on--demand from various perspectives,
and revealed a number of topics that,
through our framing, are clearly situated together.
Those topics are, at a high level, as follows:
\begin{enumerate}
\item the processes involved in making work into tasks, or \textbf{discretization};
% in ``\nameref{sec:MakingGigsWork}'';
\item the outcomes of that discretization, both on the work itself as well as the workers;
% in ``\nameref{sec:Fallout}'';
and finally
\item the results of these forces; namely the turning of work toward \textbf{factories}.
% which we will discuss in ``\nameref{sec:Factorization}''.
\end{enumerate}

@@

The HCI community is perhaps most familiar with examples of task--based work such as
99designs,
Amazon Mechanical Turk (AMT),
and increasingly
Uber \& Lyft,
which all allow requesters in various forms to tap into
resources such as
cars,
computers, and above all
``cognitive surplus''
with relative ease
\cite{howe2006rise,DillahuntPromise,storiesIraniSilberman,shirky2010cognitive}.
This insight, that
workers can be geographically distributed and tasks decomposed,
% (especially given careful central management of those workers, discussed later),
has proven remarkably compelling
and an effective fulcrum for leveraging the Internet for highly scalable work
\cite{sensitiveTasks,embracingErrorKrishna}.

@@

\subsubsection{Decomposition}\label{sec:decomposition}
Piecework may be thought of as vertically slicing work such that 
each person is responsible for the whole task
--- making a whole garment, in this case.
Broken down in this way, work could grow to unprecedented scales,
but the quality of the work would remain relatively variable.
Textile work being a salient example,
it took time for workers to acquire sufficient skill
to do every aspect of the piece work so that the garment would be accepted.
% some seamstresses might be better than others at the same task,
% making this framing of the work initially problematic.

Scholarship describing and exploring
the decomposition of tasks is perhaps the most established of the above areas among HCI researchers;
\citeauthor{bernsteinSoylent} made early contributions to this area with \textit{Soylent}
(by coining and employing the ``find--fix--verify'' approach)
\cite{bernsteinSoylent}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work might be readily interrupted
\cite{cheng2015break}.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work
by exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While this work doesn't strictly fall under ``crowdsourcing'',
the major contributions here
seem uncontroversially to be inspired by the design of crowd work.

@@

Work decomposition, then, is far from new;
``decomposition'' generally illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{silberman2010ethics} in particular foresaw this danger and warned of it in
\citeyear{silberman2010ethics}
\cite{crowdworkFuture,silberman2010ethics,nickerson2013crowd}.
In both the historical and contemporary cases of decomposed work,
work was,
at least initially,
distributed in the form of tasks to the homes of workers;
\citeauthor{riisOtherSideLives} captured this in his documentary work
\citetitle{riisOtherSideLives}
in \citeyear{riisOtherSideLives}
\cite{riisOtherSideLives}.

@@

Here, \citeauthor{hu1961parallel}'s work,
saying of assembly line work that
``it is assumed that men are of equal ability and every man can do any of the $n$ jobs'',
parallels the approach that dominated early research into crowd work
--- namely, using non--expert crowds for complex work
\cite{hu1961parallel}.
This mindset in \citeauthor{hu1961parallel}'s analysis,
and indeed the study of factory and mass manufacturing labor through the \nth{20} century,
substantively owes its existence to scientific management
and the rigorous decomposition of work into tasks, discussed earlier,
and persists to this day as it colors
researchers' goals and objectives in the study and design of crowd work.

@@

\itshape
So work output is variable, and that's bad. What are we doing about it?
Historically, this is what led to factories; you would pay some experts who understood what they needed to do
and they would form a cohort into which you invest more.

Some research already looks at stuff like investing in workers
\cite{shepherdingDow}.
What else is there that kind of goes in this direction?
Informally, we know that this happens a lot
\cite{jonBrelig}.
In fact, the formalization of factories 
% But \citeauthor{shepherdingDow}'s contribution operates at an individual scale;
% giving feedback --- even automated --- to individual workers replicates many of the same features
% (and limitations) of conventional offline work
\upshape

\section{Bleak Futures}
We've traced a path from piecework itself through
the processes that describe the design and implementation of piece work and crowd work as part of the same thread;
from there, we followed the trail from decomposition to work abstraction,
and the potential to break work away from workers themselves,
which in turn facilitates flexibility for requesters as well as workers.
\ali{oh, forgot to mention that
I want to cite something from CHI 2016 that mentioned
the flexibility that Uber/Lyft give drivers}

@@

% The insight here seems to have been that
% a substantial amount of work does not necessarily need to be done in collocated space,
% but can be done from one's own home or other space arranged by the worker.
% Moreover, by shifting the workplace into the worker's domain,
% the cost of capital involved in that work can more easily be placed on workers' backs
% \msb{I don't think that was the original motivation for AMT or Uber --- it was about reaching people who could not otherwise join the labor force for Amazon's data cleaning or for taxi-ing.}.
% I didn't mean that this was some insight that Uber or Lyft had, but that this was some part of what makes Uber work;
% i would argue categorically that these companies wouldn't functionally work if they weren't able to obviate the 
% maintenance costs that a factory owner would associate with their capital (e.g. auto costs)

% While yellow--cab organizations often manage drivers in similar ways to platforms such as Uber and Lyft
% (inasmuch as drivers are often considered contractors, or otherwise exempt from the formal status of ``employee''),
% these new systems go further
% by framing ownership and responsibility for costs
% (e.g. automotive maintenance)
% on drivers.
% In our fieldwork, we discovered many longtime ``on--demand'' drivers
% (affiliated with platforms such as Uber and Lyft)
% who readily voiced frustration with the costs of
% frequent oil changes and the unexpected replacement of expensive parts.
% Distributing labor had similar effects on pieceworkers at the turn of the \nth{20} century;
% textile workers were given the source material with which to work,
% but were generally expected to use their own sewing materials and work in their own homes
% \cite{hapke2004sweatshop}.

% \subsection{Discretization and Routinization}
% \subsubsection{Decomposition}\label{sec:decomposition}

@@

% Opening the door to more discrete modules of work known as tasks 
% % Work has become discretized in the last 10 years, particularly in the information work sector.
% Contributions such as
% ``find--fix--verify'' % (described in \citetitle{bernsteinSoylent})
% and
% ``Cascade'' % (described in \citetitle{chilton2013cascade})
% make it easier to assign smaller components of work to myriad workers and
% recompose the constituent parts into something more complex
% \cite{bernsteinSoylent,chilton2013cascade}.
% Some work has taken special interest in the process of breaking tasks down into more manageable parts
% % Some work has even turned to break it down'',
% inasmuch as decomposing what we might call ``macro'' tasks into microtasks,
% both for the purposes of crowd--sourcing in the sense of out--sourcing work
% as well as ``selfsourcing''
% \cite{cheng2015break,selfsourcingTeevan2014}.

% The parallels between this kind of work and
% historical piecework of the turn of the \nth{20} century
% is by no means new.
% 
% The \textbf{discretization} and decomposition of work certainly facilitates
% breaking tasks down,
% parallelizing work,
% and getting more done across a broader array of people;
% but the key advantage in turning macro tasks 
% into many micro tasks is that we can make that work \textit{routine}.

% routinization can be seen in the contemporary in work--flows
% \cite{foundry,bernsteinSoylent}.
% [\textit{There are various papers that talk about creating a work--flow;
% maybe this is where FFV belongs? Foundry?}].

@@

% Piecework emerged at the turn of the \nth{20} century,
% right at the time that telecommunications began to boom in the United States. % too far a reach?
% \textit{Did telecom enable remote management?}
